k-Space Domain Parallel Transmit Pulse Design

### 2020-09-07 Manuscript/Result.tex
wag results edits

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ErrorMap_2}
	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
	Normalized excitation patterns (top row) and error maps (bottom row) in central axial, sagittal and coronal slices 
	for k-space domain (left) and spatial domain designs (right).}
	\label{fig:ErrorMap}
\end{figure}
Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for spatial and k-space domain designs. 
The k-space design was performed with 16 parallel threads and patch and inclusion widths of 4. 
Both designs were performed with a 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
respectively. 
For both design methods, most of the errors appeared at the edges of the transition band, and errors elsewhere were lower than 5\% of the target flip angle. 
This indicates uniform inner volume excitation while maintaining the outer volume intact. 
The parallelized k-space domain design required 2.9 seconds computation versus 100.9 seconds for the spatial domain method, a 97\% decrease.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ComputationTime_2}
	\caption{(a) k-Space design time versus number of threads, for patch and inclusion widths of 4. 
	(b) Studies of different parallelization parameters, where patch width is the square root of the number of $\mathbf{W}$ columns solved for simultaneously and inclusion width is the assumed range of influence of each excitation k-space location. \textbf{(a)} Computation time vs. thread numbers. Patch width and inclusion with were kept at 4 cycle/FOV. \textbf{(b\&c)} Computation time (blue axis) and RMSE (red axis) vs. patch widths (b) and inclusion widths (c). Thread number were kept at 16 of for both design. Inclusion width was constant at 4 in (b) and patch widths were constant at 4 (solid line) and 8 (dashed line).}
	\label{fig:ComputationTime}
\end{figure}
Figure \ref{fig:ComputationTime}a shows the mean computation time versus different thread numbers. The k-space design problem held the patch and inclusion width constant at 4. The mean computation time decreases with increasing thread numbers before 12 threads, and then plateaus due to overhead. The thread number was conservatively chosen to be 16 for the following studies to ensure timely solutions. 
Figure \ref{fig:ComputationTime}b shows the mean computation time and the RMSE with different patch widths. The computation time increases and the RMSE decreases as the patch width increases. This was because when patch width increases, there are more excitation trajectory points included in one instance problem, even with the same inclusion width. As a result, each instance problem becomes bigger and more time consuming, which cancels the advantageous fact that there are fewer instance problems in total, especially in cases with parallel computing. Furthermore, increasing the patch width is equivalently increasing the inclusion widths for the center target points within each patch, which makes the solutions more accurate. Here, we chose patch widths 4 and 8 (labeled $2^2$ and $2^3$) to balance time and accuracy for further evaluation.
Figure \ref{fig:ComputationTime}c shows the mean computation time and the RMSE with different inclusion widths. The solid lines and dashed lines were obtained with patch width 4 and 8, respectively. Computation time increases and error decreases with increasing inclusion width. Particularly, increasing inclusion width is equivalent to utilizing more accurate $B_1^+$ information by truncating the $B_1^+$ map Fourier transforms to zero further out from DC. For both patch widths 4 and 8, 4 is the optimal inclusion width, which confirms the result in \ref{fig:ComputationTime}a , previously. Using an inclusion width of 4, the computation time and error are acceptable for both patch width numbers. Following these results,  we chose patch width 4 for the further designs.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{L_curve}
	\caption{L-curves for spatial domain and k-space domain pulse designs, 
	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Path / Inclusion Width = 4' versus `Full Patch'),
	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ matrices' versus
	`Exact $\bm{S}^H\bm{S}$ matrices').}
	\label{fig:LCurves}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{GibbsRinging_3}
	\caption{Normalized error maps and RMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid. Red arrows indicate the Gibbs ringing in low-resolution spatial domain design. \textbf{(b)} Normalized error map for spatial domain design with 3 mm iso-resolution, 64$\times$64$\times$48 design grid.}
	\label{fig:GibbsRing}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Acceleration_3}
	\caption{ \textcolor{red}{We should talk about this; I don't think reviewers will like the fact that the scale starts at 0.2. Also we should probably call it `Reduction Factor' since it is 
	really the factor by which the pulse duration is reduced, and not exactly a k-space undersampling factor, is that right?}
	Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), with excitation trajectories undersampled by different reduction factors (third row).}
	\label{fig:kspace_PTX_Acceleration}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{kspace_PTX_B0}
	\caption{\textcolor{red}{WAG: Update with new correction method; include compute times and errors versus number of segments}
	\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity. \textbf{(b)} Normalized excitation maps and RMSE for spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third rows).}
	\label{fig:kspace_PTX_B0}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ErrorMap}
	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
	Normalized excitation patterns (top row) and error maps (bottom row) in central axial, sagittal and coronal slices 
	for k-space domain (left) and spatial domain designs (right).}
	\label{fig:ErrorMap}
\end{figure}
Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for spatial and k-space domain designs. 
The k-space design was performed with 16 parallel threads and patch and inclusion widths of 4. 
Both designs were performed with a 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
respectively. 
For both design methods, most of the errors appeared at the edges of the transition band, and errors elsewhere were lower than 5\% of the target flip angle. 
This indicates uniform inner volume excitation while maintaining the outer volume intact. 
The parallelized k-space domain design required 2.9 seconds computation versus 100.9 seconds for the spatial domain method, a 97\% decrease.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ComputationTime}
	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4. 
	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 and 16 threads. 
	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 and 16 threads.}
	\label{fig:ComputationTime}
\end{figure}
Figure \ref{fig:ComputationTime}a shows the mean computation time versus different thread numbers. The k-space design problem held the patch and inclusion width constant at 4. The mean computation time decreases with increasing thread numbers before 12 threads, and then plateaus due to overhead. The thread number was conservatively chosen to be 16 for the following studies to ensure timely solutions. 
Figure \ref{fig:ComputationTime}b shows the mean computation time and the RMSE with different patch widths. The computation time increases and the RMSE decreases as the patch width increases. This was because when patch width increases, there are more excitation trajectory points included in one instance problem, even with the same inclusion width. As a result, each instance problem becomes bigger and more time consuming, which cancels the advantageous fact that there are fewer instance problems in total, especially in cases with parallel computing. Furthermore, increasing the patch width is equivalently increasing the inclusion widths for the center target points within each patch, which makes the solutions more accurate. Here, we chose patch widths 4 and 8 (labeled $2^2$ and $2^3$) to balance time and accuracy for further evaluation.
Figure \ref{fig:ComputationTime}c shows the mean computation time and the RMSE with different inclusion widths. The solid lines and dashed lines were obtained with patch width 4 and 8, respectively. Computation time increases and error decreases with increasing inclusion width. Particularly, increasing inclusion width is equivalent to utilizing more accurate $B_1^+$ information by truncating the $B_1^+$ map Fourier transforms to zero further out from DC. For both patch widths 4 and 8, 4 is the optimal inclusion width, which confirms the result in \ref{fig:ComputationTime}a , previously. Using an inclusion width of 4, the computation time and error are acceptable for both patch width numbers. Following these results,  we chose patch width 4 for the further designs.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{L_curve}
	\caption{L-curves for spatial domain and k-space domain pulse designs, 
	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Path / Inclusion Width = 4' versus `Full Patch'),
	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ Matrices' versus
	`Exact $\bm{S}^H\bm{S}$ Matrices').}
	\label{fig:LCurves}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{GibbsRinging}
	\caption{Normalized error maps and RMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid. Red arrows indicate the Gibbs ringing in low-resolution spatial domain design. \textbf{(b)} Normalized error map for spatial domain design with 3 mm iso-resolution, 64$\times$64$\times$48 design grid.}
	\label{fig:GibbsRing}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ReductionFactor}
	\caption{Normalized error maps and RMSE for spatial domain design (first row) and k-space domain design (second row), 
	using excitation k-space trajectories with different reduction factors (third row).
	The reduction factors are referenced to the 10 ms trajectory in Figure \ref{fig:Target} (second column).}
	\label{fig:kspace_PTX_Acceleration}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{OffResonance}
	\caption{\textcolor{red}{WAG: Update with new correction method; include compute times and errors versus number of segments}
	\textbf{(a)} Normalized off-resonance map with Gaussian distortion centered above the frontal sinus, mimicking a characteristic susceptibility induced $B_0$ inhomogeneity. \textbf{(b)} Normalized excitation maps and RMSE for spatial domain design with off-resonance correction (first row), k-space domain design with and without off-resonance correction (second \& third rows).}
	\label{fig:kspace_PTX_B0}
\end{figure}
